Memory-aware Adaptive Scheduling of Scientific Workflows On Heterogeneous Architectures\\

### 2024-10-09 main.tex
rough draft for second part of intro (WIP)

    %%% MOTIVATION %%%
    Today's computing platforms are often heterogeneous,

    \begin{itemize}
      \item Heterogeneous means: different CPU speeds, different mem sizes
      \item With different mem sizes: more difficult to adhere to mem constraints
      \item Adhering to memory constraints is very important to avoid execution failures.
      \item In this paper, we formulate the problem that takes memories into consideration (using (nearly the) model from ICPP paper)
      \item Objective: makespan (proxy for total execution time)
      \item HEFT (see book chapter) is one of the most popular heuristics (cite a review).
      \item However, existing HEFT variations do not take memory sizes into consideration (\skug{check in related work if true!}).
        Note: 2 papers that deal with memory sizes, but model is very different!
      \item Many scheduling strategies assume that task running times provided to them are accurate. This is not really the case
        in practice. Thus, one needs to adapt the schedule when major deviations occur (which is the case in practice).
        List-based schedulers such as HEFT are not designed for adaptation and would compute a completely schedule from scratch.
    \end{itemize}

>>>>

    %%% MOTIVATION %%%
    Modern computing platforms are often heterogeneous, meaning they feature varying CPU speeds
    and memory sizes. In general, varying memory sizes make it more challenging to compute
    a schedule that respects all memory constraints -- meaning that no task is executed on a 
    processor with less memory than needed for the task. This is, however, very important to
    avoid (possibly expensive) runtime failures and to provide a satisfactory user experience.
    Hence, building on previous related work~\cite{TODO}, we consider a scheduling problem 
    formulation that takes memory sizes as explicit constraints into account. Its objective is
    the very common \emph{makespan}, which acts as proxy for the total execution time of a
    workflow.

    \begin{itemize}
      \item HEFT (see book chapter) is one of the most popular heuristics (cite a review).
      \item However, existing HEFT variations do not take memory sizes into consideration (\skug{check in related work if true!}).
        Note: 2 papers that deal with memory sizes, but model is very different!
      \item Many scheduling strategies assume that task running times provided to them are accurate. This is not really the case
        in practice. Thus, one needs to adapt the schedule when major deviations occur (which is the case in practice).
        List-based schedulers such as HEFT are not designed for adaptation and would compute a completely schedule from scratch.
    \end{itemize}
